Boson-Sampling with Single Photons: A Roadmap to Post-Classical Computation

### 2016-10-11 paper.tex
added post-classical section

\comment{Be more bold, ambitious and futuristic. Don't just want to match and slightly improve on classical computers. We want to massively outperform the world's biggest supercomputers by orders of magnitude. Let's talk more about that regime, instead of the regime where n=4 outperforms a desktop PC. That's a really uninspiring regime to talk about. How much will technology have to improve to get us to that more ambitious level? Let's look at a Moore's Law projection and estimate where classical supercomputing is going. Then let's make a boson-sampler that's faster than the biggest supercomputer 20 years from now. Then we can actually make a claim to have entered the post-classical era!}

>>>>

Until now we have used our calculations to consider scenarios with relatively few photons, as a comparison against present-day classical PCs as a benchmark. Of course, the exciting prospect of quantum computing is not to match present-day computer technology, but to exponentially outperform it by orders of magnitude. Here we will be more ambitious and look to the future, with the goal of outperforming expected classical computer technology of the future by such margins.

In Fig.~\ref{fig:moores_law} we plot historical trends in classical computing performance for both desktop PCs and top-end supercomputers. We extrapolate 5 years into the future, using an exponential fit, to predict the future progression of computer performance.

\begin{figure}[!htb]
%\includegraphics[width=\columnwidth]{moores_law}
\caption{Extrapolation of desktop PC (bottom) and top-end supercomputer (top) performance over time, following an exponential fit, as predicted by Moore's Law.} \label{fig:moores_law}
\end{figure}

From our predictions for the performance of classical computing 5 years into the future, in Fig.~\ref{fig:outperform} we relate these predicted performances to the scattershot boson-sampling protocol, to estimate the number of photons required to match this performance. We further estimate the number of photons required to outperform these benchmarks by a factor of 10, taking us into the regime of post-classical computation.

\begin{figure}[!htb]
%\includegraphics[width=\columnwidth]{outperform}
\caption{Performance of scattershot boson-sampling, showing data-points coinciding with our expectations for desktop PC and supercomputer performance in 5 years, as well as exceeding these anticipated performances by a factor of 10, which we use as a benchmark for the \emph{post-classical era}.} \label{fig:outperform}
\end{figure}

The number of photons required for these different benchmarks are summarised in Tab.~\ref{tab:benchmark_outperform}

\begin{table*}[!htb]
\begin{tabular}{|c|c|c|c|c|}
\hline
Classical computer in 5 years & Classical FLOPS & Single-photon efficiency ($\eta$) & Photon-number ($n$) & Single-photon fidelity ($F$) \\
\hline
\hline
Desktop PC & . & 99\% & . & . \\
 & & 99.9\% & . & . \\
\hline
Desktop PC (10x) & . & 99\% & . & . \\
 & & 99.9\% & . & . \\
\hline
Supercomputer & . & 99\% & . & . \\
 & & 99.9\% & . & . \\
\hline
Supercomputer (10x) & . & 99\% & . & . \\
 & & 99.9\% & . & . \\
\hline
\end{tabular} \caption{Comparison of the classical performance of different classical computers predicted in 5 year's time, their associated performance in FLOPS, respective number of photons required by a boson-sampler to match their performance.} \label{tab:benchmark_outperform}
\end{table*}
